---
title: "A4_Q2"
author: "Joohyeok"
date: "2023-11-08"
output: html_document
---

```{r setup, include=TRUE}
library(tidyverse)

df=read.table("depression.txt",header=TRUE)
fit=lm(Depression~BMI+I(BMI^2),df)
result <- summary(fit)

```

c)
```{r}
result$coefficients

```

d) From the summary output, R^2 is 0.03649. The deterministic part of the model (the quadratic polynomial of BMI) explains 3.65% of the observed variability in depression score.
```{r}
result

```

e)
```{r}
ggplot(df,aes(x=BMI,y=Depression))+
  geom_point(size=3,colour="hotpink")+
  stat_smooth(method="lm",se=FALSE, formula=y~poly(x,2,raw=TRUE),
              colour="black",size=2)+
  labs(y="depression score", x="BMI")+
  theme_bw()+
  theme(axis.title=element_text(size=16))

```

f) i) H0: beta2=0 vs. Ha: beta2 is not equal to 0

ii) The value of the test statistic(from the summary output) is t = 7.366

iii) p-value = 2.82e-13 (from the output)

iv) Since p-value<0.01, we reject H0. We have evidence at the 1% level that depression is more serious in children who are underweight or overweight.


