---
title: "A3_Q3"
author: "Joohyeok"
date: "2023-10-30"
output: html_document
---

```{r setup, include=TRUE}
library(tidyverse)
df = read.table("LOS.txt",header=TRUE)

fit=lm(LOS~age,df)

df = df %>% mutate(Residual=resid(fit),
                   Fitted=fitted(fit))

ggplot(df,aes(y=LOS,x=age))+
  geom_point(size=4,colour="orange")+
  geom_abline(intercept=coef(fit)[1],slope=coef(fit)[2],
              linewidth=2)+
  theme_bw()+
  theme(axis.title=element_text(size=20),
        axis.text=element_text(size=14))+
  labs(x="age (in years)",y="LOS (in days)")

ggplot(df,aes(y=Residual,x=Fitted))+
  geom_point(size=4,colour="orange")+
  geom_hline(yintercept=0,linewidth=2)+
  theme_bw()+
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=14))

ggplot(df,aes(sample=Residual))+
  stat_qq(size=4,colour="orange")+
  stat_qq_line(linewidth=2)+
  labs(y="Residual", x="Theoretical Quantile")+
  theme_bw()+
  theme(axis.title=element_text(size=16))

ggplot(df,aes(x=Residual))+
  geom_histogram(fill="orange")+
  theme_bw()+
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=14))+
  labs(y="Frequency")

ggplot(df,aes(x=LOS))+
  geom_histogram(fill="orange")+
  theme_bw()+
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=14))+
  labs(y="Frequency")

```

i) Linearity seems reasonable because the residuals vs.fitted values plot does not suggest any trends.
ii) Common SD seems reasonable because for the residuals vs.fitted values plot, vertical spread is approximately constant over the range of the fitted values.
iii) Normality is questionable because the Q-Q plot shows a serious departure from the line.

The residuals are right-skewed. 
Also, the responses are right-skewed.
So, I recommend that the researcher use logarithm of LOS as the response.

```{r}
df = df %>% mutate(LogLOS=log(LOS))

fit1=lm(LogLOS~age,df)

df = df %>% mutate(Residual.log=resid(fit1),
                   Fitted.log=fitted(fit1))

ggplot(df,aes(y=LogLOS,x=age))+
  geom_point(size=4,colour="orange")+
  geom_abline(intercept=coef(fit1)[1],slope=coef(fit1)[2],
              linewidth=2)+
  theme_bw()+
  theme(axis.title=element_text(size=20),
        axis.text=element_text(size=14))+
  labs(x="age (in years)",y="LOG Length of Stay (in days)")


ggplot(df,aes(y=Residual.log,x=Fitted.log))+
  geom_point(size=4,colour="orange")+
  geom_hline(yintercept=0,linewidth=2)+
  labs(y="Residual",x="Fitted")+
  theme_bw()+
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=14))

#Create the normal quantile plot of the residuals:
ggplot(df,aes(sample=Residual.log))+
  stat_qq(size=4,colour="orange")+
  stat_qq_line(linewidth=2)+
  labs(y="Residual", x="Theoretical Quantile")+
  theme_bw()+
  theme(axis.title=element_text(size=16))

```

i) Linearity seems reasonable because the residuals vs. fitted values plot does not suggest any trends.
ii) Common SD seems reasonable because for the residuals vs. fitted values plot, vertical spread is approximately constant over the range of the fitted values.
iii) Normality is much closer to reasonable because for the Q-Q plot, minor departures from the line are likely not serious. 

```{r}
pi=predict(fit1,newdata=data.frame(age=40),interval="prediction",level=0.95)
pi
exp(pi)
```
b) Using the model with logarithm of LOS as the response, a 95% prediction interval for the LOS of a 40 year old patient is (0.513, 7.589).
